Nonzero Mean ASH

### 2014-09-10 issues/issue21/Ash Nonzeromean.rmd
Documentation updated,nonzeroMean method updated

---
title: "Nonzero Mean ASH"
author: "Chaoxing Dai"
date: "2014-Sep-03"
output: pdf_document
---

#Likelihood

@@

#EM Algorithm

@@

>>>>

---
title: "Nonzero Mean ASH"
author: "Chaoxing Dai"
date: "2014-Sep-10"
output: pdf_document
---

#Normal mixture with normal likelihood
```
df=NULL,mixcompdist="normal"
```
##Likelihood

@@

##EM Algorithm

@@

#Uniform mixture with Normal likelihood
```
df=NULL,mixcompdist="uniform"
```
##Likelihood
We know that the convolution of a uniform distribution and a normal would be of the following form  
$f(x)\sim N(x;\mu,\sigma^{2})$  
$g(y) \sim U(y;a,b)$  
$(f*g)(z)=\frac{1}{b-a}[\Psi_{0}(\frac{z-a-\mu}{\sigma})-\Psi_{0}(\frac{z-b-\mu}{\sigma})]$  
Where $\Psi_{0}(\cdot)$ is the cdf for standard normal distribution.

By assuming a unimodal distribution, we have the hierarchical model being the following:  
$$\beta _{j}\sim g(.) \sim \sum_{k=1}^{K} \pi _{k}f_{k}(.) \sim\sum_{k=1}^{K} \pi _{k} U(\cdot ;-\sigma_{k}+\mu,\sigma_{k}+\mu)$$

$$=\prod_{j=1}^{n} \sum_{k=1}^{K} \pi_{k}
\frac{1}{2\sigma_{k}}[\Psi_{0}(\frac{\widehat{\beta}_{j}+\sigma_{k}-\mu}{s_{j}})-\Psi_{0}(\frac{\widehat{\beta}_{j}-\sigma_{k}-\mu}{s_{j}})]$$

##EM Algorithm

$$p(x_{j},z_{j} \mid \mu,\pi )=\prod_{k=1}^{K} [\pi_{k} \frac{1}{2\sigma_{k}}[\Psi_{0}(\frac{\widehat{\beta}_{j}+\sigma_{k}-\mu}{s_{j}})-\Psi_{0}(\frac{\widehat{\beta}_{j}-\sigma_{k}-\mu}{s_{j}})]]^{I_{z_{j}}=k}$$

$$log p(x_{j},z_{j} \mid \mu,\pi )=\sum_{k=1}^{K} [I_{z_{j}}=k] log [\pi_{k} \frac{1}{2\sigma_{k}}[\Psi_{0}(\frac{\widehat{\beta}_{j}+\sigma_{k}-\mu}{s_{j}})-\Psi_{0}(\frac{\widehat{\beta}_{j}-\sigma_{k}-\mu}{s_{j}})]]$$

$$=\sum_{k=1}^{K} [I_{z_{j}}=k] [log \pi_{k}-log(2\sigma_{k}) +log [\Psi_{0}(\frac{\widehat{\beta}_{j}+\sigma_{k}-\mu}{s_{j}})-\Psi_{0}(\frac{\widehat{\beta}_{j}-\sigma_{k}-\mu}{s_{j}})]] $$

$$\omega_{jk}=p(z_{j}=k \mid x_{j},\pi,\mu)=\frac{\frac{1}{2\sigma_{k}}[\Psi_{0}(\frac{\widehat{\beta}_{j}+\sigma_{k}-\mu}{s_{j}})-\Psi_{0}(\frac{\widehat{\beta}_{j}-\sigma_{k}-\mu}{s_{j}})]}
{\sum_{l=1}^{K}\frac{1}{2\sigma_{l}}[\Psi_{0}(\frac{\widehat{\beta}_{j}+\sigma_{l}-\mu}{s_{j}})-\Psi_{0}(\frac{\widehat{\beta}_{j}-\sigma_{l}-\mu}{s_{j}})]}$$

$$Q=E_{Z\mid X,\mu, \pi}[log\,p(X,Z \mid \mu,\pi )]=\sum_{j=1}^{n}\sum_{k=1}^{K} [\omega_{jk}]
 [log \pi_{k}-log(2\sigma_{k}) +log [\Psi_{0}(\frac{\widehat{\beta}_{j}+\sigma_{k}-\mu}{s_{j}})-\Psi_{0}(\frac{\widehat{\beta}_{j}-\sigma_{k}-\mu}{s_{j}})]] $$

The maximization over $\mu$ no longer has a closed form, and we will use the one-dimensional R optimization function $optim()$ to perform the M step.

For $\pi$, we have the same expression as before.

#Other cases
```
df=NULL,mixcompdist="halfuniform"
df=scalar,mixcompdist="normal"
df=scalar,mixcompdist="uniform"
df=scalar,mixcompdist="halfuniform"
```

Similar to the second one, as we do not have closed form solution for $\mu$ in the M step of EM algorithm, would use optimization function with SQUAREM, and a lot of functions in EMest will be re-used.
